Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-09-07 ms/main.tex
coexistence figure updates

%%% Figure: coexistence map - without oblique transmission
\begin{figure}[htb]
\centering
\includegraphics{coexistence_without_oblique.pdf}
\caption{\textbf{Stable and unstable coexistence between cooperation and defection without oblique transmission.}
  The curves show the frequency of the cooperative phenotype $A$ among parents in the next generation $\tilde{p}'$ vs. the current generation $\tilde{p}$ (\autoref{eq:nextgen_parents_vertical_only}).
  The dashed black line is $\tilde{p}'=\tilde{p}$.
  The curves and the dashed line intersect at the polymorphic equilibrium $\tilde{p}^*$ (black circle).
  When the curves are above the dashed line, $\tilde'{p}>\tilde{p}$, then $\tilde{p}$ increase.
  When the curves are below the dashed line, $\tilde'{p}<\tilde{p}$, then $\tilde{p}$ decreases.
  The yellow curve, for which the polymorphic equilibrium is stable, is given by $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, and $\alpha = 0.45$, which give $\gamma_2<c<\gamma_1$ (\autoref{eq:cost_boundaries})
  The blue curve, for which the equilibrium is unstable, is given by $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, and $\alpha = 0.4$, which give $\gamma_1<c<\gamma_2$.
  In both cases there is no oblique transmission, $v=1$; see \autoref{fig:coexistence_with_oblique} for $v<1$.
  }
\label{fig:coexistence_without_oblique}
\end{figure}

@@

%%% Figure: coexistence map - without oblique transmission
\begin{figure}[htb]
  \centering
  \includegraphics{coexistence_with_oblique.pdf}
  \caption{\textbf{Stable coexistence between cooperation and defection with oblique transmission.}
  The curve shows the frequency of the cooperative phenotype $A$ among juveniles in the next generation $\hat{p}'$ vs. the current generation $\hat{p}$ (\autoref{eq:horizontal}).
  The dashed black line is $\hat{p}'=\hat{p}$.
  The curve and the dashed line intersect at the stable equilibrium $\hat{p}^*$ (black circle).
  When $\hat{p} < \hat{p}^*$ then the curve is above the dashed line, $\hat{p}' > \hat{p}$, and $\hat{p}$ increases towards $\hat{p}^*$.
  When $\hat{p} > \hat{p}^*$ then the curve is below the dashed line, $\hat{p}' < \hat{p}$, and $\hat{p}$ decreases towards $\hat{p}^*$.
  Here,  $T_A = 0.4$, $T_B = 0.9$, $b = 20$, $c=0.1$, $\alpha = 1$, and $v=0.4$, which give $0<\beta_3<\beta_1$ (\autoref{eq:polynomial_coefficients}).
  }
  \label{fig:coexistence_with_oblique}
  \end{figure}

>>>>

%%% Figure: coexistence map - without oblique transmission
\begin{figure}[htb]
\centering
\includegraphics{coexistence_without_oblique.pdf}
\caption{\textbf{Stable and unstable coexistence between cooperation and defection without oblique transmission.}
  The curves show the frequency of the cooperative phenotype $A$ among parents in the next generation $\tilde{p}'$ vs. the current generation $\tilde{p}$ (\autoref{eq:nextgen_parents_vertical_only}).
  The dashed black line is $\tilde{p}'=\tilde{p}$.
  The curves and the dashed line intersect at the polymorphic equilibrium $\tilde{p}^*$ (black circle).
  When the curves are above the dashed line, $\tilde'{p}>\tilde{p}$, then $\tilde{p}$ increase.
  When the curves are below the dashed line, $\tilde'{p}<\tilde{p}$, then $\tilde{p}$ decreases.
  The orange curve, for which the polymorphic equilibrium is stable, is given by $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, and $\alpha = 0.45$, which give $\gamma_2<c<\gamma_1$ (\autoref{eq:cost_boundaries})
  The blue curve, for which the equilibrium is unstable, is given by $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, and $\alpha = 0.4$, which give $\gamma_1<c<\gamma_2$.
  In both cases there is no oblique transmission, $v=1$; see \autoref{fig:coexistence_with_oblique} for $v<1$.
  }
\label{fig:coexistence_without_oblique}
\end{figure}

@@

%%% Figure: coexistence map - with oblique transmission
\begin{figure}[htb]
  \centering
  \includegraphics{coexistence_with_oblique.pdf}
  \caption{\textbf{Stable coexistence between cooperation and defection with oblique transmission.}
  The curve shows the frequency of the cooperative phenotype $A$ among juveniles in the next generation $\hat{p}'$ vs. the current generation $\hat{p}$ (\autoref{eq:horizontal}).
  The dashed black line is $\hat{p}'=\hat{p}$.
  The curve and the dashed line intersect at the stable equilibrium $\hat{p}^*$ (black circle).
  When $\hat{p} < \hat{p}^*$ then the curve is above the dashed line, $\hat{p}' > \hat{p}$, and $\hat{p}$ increases towards $\hat{p}^*$.
  When $\hat{p} > \hat{p}^*$ then the curve is below the dashed line, $\hat{p}' < \hat{p}$, and $\hat{p}$ decreases towards $\hat{p}^*$.
  Here,  $T_A = 0.4$, $T_B = 0.9$, $b = 20$, $c=0.1$, $\alpha = 1$, and $v=0.4$, which give $0<\beta_3<\beta_1$ (\autoref{eq:polynomial_coefficients}).
  }
  \label{fig:coexistence_with_oblique}
  \end{figure}
